---
title: "Random Analyses for Pilot 3.1"
author: "Haoyang"
date: today
date-format: full
format: 
    html:
        toc: true
        embed-resources: true
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r}
#| include: false
library(here)
library(tidyverse)
library(afex)
library(emmeans)
set_sum_contrasts()

vigour_data <- read_csv(here("data", "pilot3.1_vigour_data.csv"),
                        col_types = cols(version = col_character())) %>% 
    mutate(magnitude = factor(magnitude, levels = c(1, 2, 5), ordered = T),
           ratio = factor(ratio, levels = c(1, 8, 16), ordered = T)) %>%
    mutate(
        response_times = str_extract_all(response_times, "\\d+"),
        response_times = map(response_times, as.numeric)
    ) %>% 
    filter(version != "3.2")
vigour_data 

```

```{r}
info_files <- list.files(here("data", "prolific_participant_info"), pattern = ".*\\.csv", full.names = T)
info_data <- read_csv(info_files) %>% 
    filter(Age != "CONSENT_REVOKED") %>% 
    rename(prolific_id = `Participant id`) %>% 
    mutate(age = as.numeric(Age))
```

```{r}
vigour_data %>% 
    group_by(prolific_id, version) %>% 
    summarize(unit_n_presses = mean(trial_presses * 1000 / trial_duration)) %>%
    replace_na(list(version = 3.1)) %>% 
    mutate(version = as.character(version)) %>% 
    ungroup() %>% 
    left_join(info_data) %>% 
    ggplot(aes(x = age, y = unit_n_presses)) +
    geom_point(alpha = 0.3) +
    geom_smooth(method = "lm")

```

## Number of presses vs. FR & Magnitude

```{r}
vigour_mixed <- 
    mixed(avg_trial_presses ~ magnitude * ratio + (magnitude * ratio | prolific_id),
          data = vigour_data %>% mutate(across(c(magnitude, ratio), ~ factor(., ordered = F))) %>% mutate(avg_trial_presses = trial_presses * 1000 / trial_duration),
          method = "S") 
vigour_mixed

vigour_mixed %>% 
    afex_plot(x = "ratio",
              trace = "magnitude",
              error = "within",
              mapping = "color",
              error_ci = F, 
              data_alpha = 0.1) +
    scale_color_viridis_d() +
    coord_cartesian(ylim = c(4, 5.5)) +
    theme_minimal()
```

### ICC: measurement reliability, or "repeatability"

```{r}
performance::icc(vigour_mixed, tolerance = 0)

```

## Post-vigour test

```{r}
vigour_test_data <- read_csv(here("data", "pilot3.1_vigour_test_data.csv")) %>% 
    mutate(across(starts_with("diff_"), ~ as.vector(scale(.x)))) %>% 
    mutate(choice_left = as.integer(response == "ArrowLeft"))

vigour_test_glmer1 <- glmer(choice_left ~ diff_mag + diff_fr_rel + diff_rpp + (diff_mag + diff_fr_rel + diff_rpp | prolific_id), data = vigour_test_data, family = binomial(), control = glmerControl(optimizer = "bobyqa"))

summary(vigour_test_glmer1)

vigour_test_glmer2 <- glmer(choice_left ~ diff_mag + diff_fr_abs + diff_rpp + (diff_mag + diff_fr_abs + diff_rpp | prolific_id), data = vigour_test_data, family = binomial(), control = glmerControl(optimizer = "bobyqa"))

summary(vigour_test_glmer2)

```

```{r}
anova(vigour_test_glmer1, vigour_test_glmer2)
```

When comparing these two models, using absolute difference between fixed ratios would have better model performance (e.g., lower AIC/BIC, higher model evidence). This suggest that participants tended to compare the two options based on the scale of absolute difference rather than relative difference. On the absolute scale, FRs of 1, 8, and 16 have very similar differences between two consecutive ones; yet on the relative scale, 1 and 8 have three times of difference as 8 and 16.

This also could be good thing as it could somehow enlarge the condition difference?

```{r}
vigour_test_rpp <- glmer(choice_left ~ diff_rpp + (diff_rpp | prolific_id), data = vigour_test_data, family = binomial(), control = glmerControl(optimizer = "bobyqa"))

predict(vigour_test_rpp, vigour_test_data, type = "response") %>% 
    as_tibble()
```
